OpenMPIR

### 2017-09-06 paper.tex
Small intro change

When writing task-parallel programs today, one has a large selection of
programming models. Unfortunately, despite having significant overlap in
semantics, parallel programming models like OpenMP, Cilk, Kokkos, HPX, Charm++,
Qthreads, pthreads, MPI, Chapel, UPC, etc. have virtually no ability to
interoperate, both at compile time and run time. In addition, many of these
programming models are implemented as libraries, and therefore have no compiler
support. There has been some recent work on specializing compilers to reason
about libraries \cite{kokkos}, but the fragmentation among the models that
presents another challenge for compiler writers, which must choose a single
model to analyze and optimize. An ideal solution would be some some form of
common representation of parallelism that all IRs can share.

Internal representations (IRs) are the compiler objects on which almost all
analyses and optimizations are performed. Historically, a major drawback for
parallel codes is that IRs don't have the ability to represent, and therefore
reason about, parallelism. This prevents the application of common
optimizations to concurrent code. The recent work of Schardl et al.
\cite{shardl2017} has shown that standard compiler IRs can be extended to
represent fork-join parallelism. In that work, by extending the LLVM
instruction set with three instructions, they are able to capture all of the
semantics to implement the semantics of Cilk, an extension to C. They suggested
that a similar approach could be taken with OpenMP tasks.

>>>>

When writing task-parallel programs today, one has a large selection of
programming models. Unfortunately, despite having significant overlap in
semantics, parallel programming models like OpenMP, Cilk, Kokkos, HPX, Charm++,
Qthreads, pthreads, MPI, Chapel, UPC, etc. have virtually no ability to
interoperate, both at compile time and run time. In addition, many of these
programming models are implemented as libraries, and therefore have no compiler
support. There has been some recent work on specializing compilers to reason
about libraries \cite{kokkos}, but fragmentation among models presents a
significant challenge for compiler writers, which must choose a single model to
analyze and optimize. An ideal solution would be some some form of common
representation of parallelism that all IRs can share.

Internal representations (IRs) are the compiler objects on which almost all
analyses and optimizations are performed. Historically, a major drawback for
parallel codes is that IRs don't have the ability to represent, and therefore
reason about, parallelism. This prevents the application of common
optimizations to concurrent code. The recent work of Schardl et al.
\cite{shardl2017} has shown that real world compiler IRs can be extended to
represent fork-join parallelism. By extending the LLVM instruction set with
three instructions, they were able to capture all of the semantics to implement
the semantics of Cilk, an extension to C. They suggested that a similar
approach could be taken with OpenMP tasks.
